Temporal Split

### 2023-01-24 workflow/notebooks/temporal-split.Rmd
Bump date
Write rules to train temporal split models

---
title: "Temporal Split"
date: 2022-12-16
output: 
  github_document:
    html_preview: false
---

@@

```{r int_props}
test_dat_int <- metadat_int %>% 
  arrange(desc(collection_date)) %>% 
  slice_max(order_by = collection_date, prop = 0.2)

>>>>

---
title: "Temporal Split"
date: 2022-01-19
output: 
  github_document:
    html_preview: false
---

@@

```{r int_props}
test_dat_int <- metadat_int %>% 
  slice_max(order_by = collection_date, prop = 0.2)
